Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

In this section, we present the results using our neural network model moving from simpler to more realistic but also more complex scenarios. We consider four types of scenarios: (i) static scenarios, where the phone is fixed at a given azimuth and pitch at a distance of 4 m in front of the AP, (ii) controlled mobility scenarios, where the phone moves along one dimension (azimuth, pitch, or slide) at a given speed keeping the other two dimensions constant, (iii) random mobility scenarios, where the phone simultaneously moves along all three dimensions at different speeds, and (v) real applications scenarios, where we use 2 real application traces -- VR and ABR video streaming -- instead of backlogged TCP traffic generate by nuttcp, under random mobility.

@@

We first analyze the impact of the phone staying within the AP's field of view (FoV). The phone faces the AP from a distance of 4 meters, and we rotate the phone to change its azimuth with respect to the AP. Fig.~\ref{} plots the throughput at the phone when the phone is rotated to the different angles. Our experiments show that when the azimuth is within [-75\degree, 75\degree], the average throughput is always $\sim$1.5 - 1.6 Gbps. Once the azimuth moves outside this region, the throughput quickly drops to 0, meaning that the AP fails to find a stable transmit sector at this angle as the phone's omnidirectional receive beam is out of the FoV of the AP. This agrees with the findings by the authors of~\cite{wei:mobicom2017}. Following this, in the rest of the paper we only focus on predicting throughput when the phone is within the AP's FoV.

>>>>

In this section, we present the results using our neural network model
moving from simpler to more realistic but also more complex
scenarios. We consider four types of scenarios: (i) {\em static} scenarios,
where the phone is fixed at a given azimuth and pitch at a distance of
4 m in front of the AP, (ii) {\em controlled mobility} scenarios, where the
phone moves along one dimension (azimuth, pitch, or slide) at a given
speed keeping the other two dimensions constant, (iii) {\em random mobility}
scenarios, where the phone simultaneously moves along all three
dimensions at different speeds, and (v) real applications scenarios,
where we use 2 real application traces -- VR and ABR video streaming
-- instead of backlogged TCP traffic generate by nuttcp, under random
mobility.

@@

We first analyze the impact of the phone staying within the AP's field
of view (FoV). The phone faces the AP from a distance of 4 meters, and
we rotate the phone to change its azimuth with respect to the
AP. Fig.~\ref{???} plots the throughput at the phone when the phone is
rotated to different angles. Our experiments show that when the
azimuth is within [-75\degree, 75\degree], the average throughput is
always $\sim$1.5 - 1.6 Gbps. Once the azimuth moves outside this
region, the throughput quickly drops to 0, meaning that the AP fails
to find a stable transmit sector at this angle as the phone's
omnidirectional receive beam is out of the FoV of the AP. This agrees
with the findings by the authors of~\cite{wei:mobicom2017}. Following
this, in the rest of the paper, we only focus on predicting throughput
when the phone is within the AP's FoV.
